---
title: "Our World in Data: Key Crop Yields"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Our World in Data: Key Crop Yields}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(cwdata)
library(ggplot2)
library(tidyverse)
```

# Description

This data set is about the world's key crop fields from 1961 to 2018. The data source is [Our World in Data](URL). It has `nrow(key_crop_yields)` rows and `ncol(key_crop_yields)` columns. The variables are about ... You can take a look of the data as below.

```{r}
key_crop_yields
```


# Examples

Examples with ggplots demonstrating how to use the package functions/datasets.

We could explore which kind of key crops has the highest production.

```{r bar}
key_crop_yields %>% 
  filter(year == 2017) %>% 
  group_by(crop) %>% 
  summarise(tonnes_per_hectare = sum(tonnes_per_hectare, na.rm = TRUE)) %>% 
  ggplot(aes(x = forcats::fct_reorder(crop, desc(tonnes_per_hectare)), 
             y = tonnes_per_hectare)) + 
  geom_col() + 
  theme_bw() + 
  labs(x = "Crop", y = "Tonnes per hectare", title = "World's key crops production in 2017", caption = "Potatoes has the highest production")
```
